---
title: "R Notebook"
output: html_notebook
---

With thanks to flowingdata for original pointer.
http://www.citizen-statistician.org/2020/05/dipping-my-toes-in-generative-art-with-my-sister/

https://generative.substack.com/p/generative-art-and-r

```{r}
#devtools::install_github("cutterkom/generativeart")
#install.packages("flametree")
#devtools::install_github("thomasp85/ambient")
#devtools::install_github("djnavarro/jasmines")
#devtools::install_github("marcusvolz/mathart")

library(aRtsy)
library(generativeart)
library(flametree)
library(jasmines)
library(mathart)
```

From jasmines package
```{r}
use_seed(1) %>%
  entity_circle(grain = 1000) %>%
  unfold_tempest(iterations = 10) %>%
  style_ribbon(background = "wheat")

```

```{r}
flametree_grow(seed = 2, trees = 3) %>% 
  flametree_plot(style = "voronoi")


flametree_grow(seed = 84, trees = 8) %>% 
  flametree_plot(style = "voronoi")

```
from aRtsy (probably nicest easy use)
```{r}
canvas_collatz(colors = '#ff2305', background = '#b2b2b2', n = 40, 
               angle.even = 0.0075, angle.odd = 0.0145, side = TRUE)

set.seed(18)
canvas_segments(colors = colorPalette('dark1'), background = '#f09d38', n = 1000, p = 0.5, H = 0.1)

#the below is red, green, orange, grey, green.  fcfcfb is off quite
pal <- jasmines::palette_manual('#ff2305','#32cd32','#f09d38','#b2b2b2','#09D36A')
#color(blue) uses the color: #0f4beb
#color(rich blue) uses the color: #0d41d1

set.seed(18)
canvas_segments(colors = c('#ff2305','#32cd32','#f09d38','#b2b2b2','#0f4beb','#0d41d1'), background = '#fcfcfb', n = 1000, p = 0.5, H = 0.1)



canvas_squares(colors = c('#ff2305','#32cd32','#f09d38','#b2b2b2','#0f4beb','#0d41d1'),

               
set.seed(6)

canvas_squares(colors = c('#ff2305','#b2b2b2','#0f4beb'),
               cuts = 100, ratio = 1.1, width = 100, height = 100)
```

#Colour notes
#Our blue is 0f4beB
#Our light grey is ebebeb
#Our red is ff2305 
#Our mid-grey is b2b2b2
#Our dark-grey is 323232

#And black 00000
#White ffffff

#If needed use a green 09D36A
#and orange FF9B00


#color(white) uses the color: #fff
#color(rich black) uses the color: #000
#color(black) uses the color: #323232
#color(blue) uses the color: #0f4beb
#color(rich blue) uses the color: #0d41d1
#color(red) uses the color: #ff2305
#color(dark grey) uses the color: #767676
#color(gun metal grey) uses the color: #707070
#color(darker grey) uses the color: #595959
#color(grey) uses the color: #b2b2b2
#color(light grey) uses the color: #ebebeb
#color(medium grey) uses the color: #7a7a7a
#color(mid-light grey) uses the color: #ccc
#color(extra-light grey) uses the color: #ddd
#color(super-light grey) uses the color: #f5f4f5
#color(ultra-light grey) uses the color: #f1f1f1
#color(green) uses the color: #32cd32
#color(orange) uses the color: #f09d38
#color(off white) uses the color: #fcfcfb

